\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-07-29 NAR_DRAFT.tex
simulation results

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with $\mu$, auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\textwidth}{@{}lllllllll@{}}
\toprule
Depth & Signature & $\mu/\beta$ & AUROC &  & AUPRC & & ICI & 
\\
& & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
\\
\colrule
100X whole genome & Concentrated & 3.6e-7 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Intermediate & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Diffuse & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
500X whole exome & Concentrated & Row 1 & .848 & .928 & .674 & .757 & .0585 & .0465
\\
500X whole exome & Intermediate & Row 1 & .847 & .842 & .677 & .707 & .0587 & .0566 
\\
500X whole exome & Diffuse & Row 1 & .850 & .873 & .676 & .698 & .0565 & .0575
\\
AML 31 & Actual & 3.6e-8 & .935 & .949 & .995 & .996 & 0.121 & 0.155
\\
\botrule
\end{tabular*}%
}
{$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
\end{table*}

>>>>

The heart of \batcave, the context-dependent prior probability of mutation, depends on the prior converging to a good representation of the data generating distribution within the set of high-confidence mutations.
We use the Kullback-Leibler divergence as a measure of the distance (or entropy difference) between the estimated prior and the actual simulated data generating distribution.
In Figure \ref{NAR-sigfig} \textbf{e)} and \textbf{f)} we order mutations by descending MuTect probability value, and compute the KL divergence between the prior after adding each mutation and the data generating distribution.
For both whole exome and whole genome the prior converges to the data generating distribution easily within the number of available high-confidence mutations.

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with $\mu$, auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\textwidth}{@{}lllllllll@{}}
\toprule
Depth & Signature & $\mu/\beta$ & AUROC &  & AUPRC & & ICI & 
\\
& & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
\\
\colrule
100X whole genome & Concentrated & 3.6e-7 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Intermediate & 3.2e-7 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Diffuse & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
500X whole exome & Concentrated & Row 1 & .848 & .928 & .674 & .757 & .0585 & .0465
\\
500X whole exome & Intermediate & Row 1 & .847 & .842 & .677 & .707 & .0587 & .0566 
\\
500X whole exome & Diffuse & Row 1 & .850 & .873 & .676 & .698 & .0565 & .0575
\\
AML 31 & Actual & 3.6e-8 & .935 & .949 & .995 & .996 & 0.121 & 0.155
\\
\botrule
\end{tabular*}%
}
{$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
\end{table*}
